A Simple Minibatch Acceptance Test for MCMC

### 2016-05-19 nips_2016.tex
exp3

In this experiment, we apply about minibatch MH testing with SGHMC (Stochastic Gradient Hamiltonian
Monte Carlo~\cite{sghmc_2014}) proposer to sample the parameter instances from a fully connected
neural network. We use Higgs data set from University of California Irvine. It is a classification
problem to distinguish between a signal process which produces Higgs bosons and a background process
which does not. We build a 4 layers neural network to tackle this problem. The first layer is a
input layer, the last layer is a softmax layer, the intermediate layers are linear followed by
Sigmoid, norm, dropout, starting and ending with linear operation.

@@

Figure~\ref{fig:nnet_fig} illustrates our experiment results.

\begin{figure}[t]
    \centering
    \includegraphics[width=1\linewidth]{exp3}
    \caption{TODO This will hopefully show results for neural networks on BIDMach.}
    \label{fig:nnet_fig}
    %\vspace{-10pt}
\end{figure}

>>>>

In this experiment, we apply about minibatch MH testing with SGHMC (Stochastic Gradient Hamiltonian
Monte Carlo~\cite{sghmc_2014}) proposer to sample the parameter instances from a fully connected
neural network. We use Higgs data set from University of California Irvine. We build a 4 layers neural network to tackle this problem. The first layer is a
input layer, the last layer is a softmax layer, the intermediate layers are linear followed by
Sigmoid, norm, dropout, starting and ending with linear operation.

@@

Figure~\ref{fig:nnet_fig} illustrates our experiment results. Fig~\ref{fig:nnet_fig}a reveals that SGHMC with our mini batch MH testing achieves high log likelihood than the baseline. But by comparing the SGHMC with and without our mini batch testing, the benefits are limited. Because we decrease the stepsize quickly, so accept rate of SGHMC is very high that the benefits of testing are not obvious.

\begin{figure}[t]
    \centering
    \includegraphics[width=1\linewidth]{exp3}
    \caption{Log likelihood vs number of passes for optimization of neural network}
    \label{fig:nnet_fig}
    \vspace{-10pt}
\end{figure}
